Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-11-01 refreport/response.tex

Regarding test problems, the referee's comment is:

\begin{verbatim}
However, the paper is let down due to the lack of tests presented for
many of the algorithms presented in the paper. In particular, the only
test presented for the MHD algorithm is the Orszag-Tang vortex test,
which 'does not seem to be extremely discriminating for MHD
algorithms' (Stone et al., 2008). In addition, results from some
tests, such as the photo-evaporation test, do not seem to be properly
compared to prior results in the literature (e.g. Jiang et
al. 2012). Finally, no tests appear to be presented for some tests
entirely, e.g. the Chemistry algorithms presented in Section 6.1.
\end{verbatim}

We have modified the test problem section as follows:

\begin{itemize}
\item We have added a section (11.2.10) showing how both \enzo\ MHD
  algorithms perform on the standard Brio \& Wu shock tube test
  problem, which is a standard test of MHD solvers.  Both \enzo\ MHD
  algorithms match the reference solution to high precision.  We retain the
  Orszag-Tang Vortex test as we feel that it is interesting to the
  intended audience.

@@

\begin{enumerate}
\item  We have corrected a typo in the equation describing the Jeans
  length refinement criterion (Equation 29).

\item We have corrected a typo in Table 4, where two photoionization
  rates were accidentally switched in the submitted version.

\item We have added missing acknowledgments.

\item We have updated the mercurial changeset hash to correspond to
  the \enzo\ 2.3 release (which was done slightly after the submission
  of the paper to ApJ).

### 2013-11-06 introduction.tex

There have been a number of numerical methods described in the
astronomical literature that contain elements of SAMR or have a
similar aim. For example, the N-body solver developed by
\citet{Villumsen89} used non-adaptive meshing to increase the
resolution in pre-selected regions. This static approach was later
used extensively when applied to hydrodynamics
\citep[e.g.,][]{Ruffert94, Anninos94}. Adding adaptivity is a more
recent enhancement, and there are now a number of codes that possess
this feature, both with and without hydrodynamics \citep{Couchman91,
Jessop94, Suisalu95, Splinter96, Gelato97, ART97, Truelove98,
flash_method, MLAPM01, Yahagi01, RAMSES, Quilis04, Ziegler05, Zhang06,
Astrobear09, Pluto-amr, GAMER, Nyx}. Of these, perhaps the most
comparable and widely used are FLASH \citep{flash_method}, which uses
grid blocks of fixed size, and RAMSES \citep{RAMSES} and ART
\citep{ART97}, both of which refine individual cells. It is also
possible to deform the grid to obtain high resolution
\citep[e.g.,][]{Gnedin95, Xu97, Pen98}, and more recently a few codes
have adopted an unstructured approach based on a moving Voronoi mesh
\citep{Arepo10, Tess11}.

>>>>

There have been a number of numerical methods described in the
astronomical literature that contain elements of SAMR or have a
similar aim. For example, the N-body solver developed by
\citet{Villumsen89} used non-adaptive meshing to increase the
resolution in pre-selected regions. This static approach was later
used extensively when applied to hydrodynamics
\citep[e.g.,][]{Ruffert94, Anninos94}. Adding adaptivity is a more
recent enhancement, and there are now a number of codes that possess
this feature, both with and without hydrodynamics \citep{Couchman91,
Jessop94, Suisalu95, Splinter96, Gelato97, ART97, Truelove98,
flash_method, MLAPM01, Yahagi01, RAMSES, Quilis04, Ziegler05, Zhang06,
CHARM, Astrobear09, Pluto-amr, GAMER, Nyx}. Of these, perhaps the most
comparable and widely used are FLASH \citep{flash_method}, which uses
grid blocks of fixed size, and RAMSES \citep{RAMSES} and ART
\citep{ART97}, both of which refine individual cells. It is also
possible to deform the grid to obtain high resolution
\citep[e.g.,][]{Gnedin95, Xu97, Pen98}, and more recently a few codes
have adopted an unstructured approach based on a moving Voronoi mesh
\citep{Arepo10, Tess11}.
